Influence of Connectivity on Dung Beetle Communities

### 2025-05-29 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
image in rmd

```{r Table1, echo=FALSE,message = FALSE,warning=FALSE}
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

>>>>

![Dung beetle secies richness in three different --- and the forest matrix surrounding patches.](images/sp_richness_patches.png){height=100%}

<!-- ```{r sp_richness_patches, echo = FALSE, fig.cap = "Dung beetle secies richness in three different --- and the forest matrix surrounding patches.", out.width = '100%'} -->
<!-- knitr::include_graphics("./corridor_beetles/corridor_docs/eric_ms_thesis/images/sp_richness_patches.png") -->
<!-- ``` -->

\newpage
```{r Table1, echo=FALSE,message = FALSE,warning=FALSE}
# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
